{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}

### 2024-09-07 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, sync

\section{Introduction}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method (PPM) applied to an upper surrogate function, and then a lower surrogate function. 
    Inspired by the interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex whose proximal mapping can be evaluated exactly for algorithm implementations. 
    As a major extension, our work describes the method of proximal gradient using the PPM interpretations. We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof. Finally, we derive major variants of the accelerated gradient (AG) and find the match of the stepsize parameters in the PPM form. 
    \par
    Some of the earlier examples for the extension of the Nesterov acceleration method make use of the classical analysis introduced by Nestrov. 
    It uses the Nesterov acceleration sequence. 
    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and a specific format of the Nesterov's estimating sequence to accomodate the proof. 
    In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
    It uses a lemma from Moreau envelope for the Lypunov analysis.
    The interpration allows choices of undetermined parameters to encompass several variants of the Nesterov accelerated gradient algorithm. 
    Ahn and Sra's approach is inspired by works from Defazio \cite{defazio_curved_2019}, Zeyuan and Lorenzo \cite{allen-zhu_linear_2016}. 
    Instead of a mirror descent step on the dual, they propose an alternative without the gradient of the dual. 
    \par
    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$ using Bregman Divergence. 
    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
    For a variant of accelerated gradient where the iterates converge, see Chambolle and Dossal \cite{chambolle_convergence_2015}. 
    Extension such as the Harpen acceleration for the resolvent operator of a maximally monotone opreator in general is outside of the scope since it not all maximal monotone operator corresponds to a subgradient operator. 
    \par
    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
    The dynamical system interpretation of the algorithm leads to the valuable insight that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function. 
    In work by \cite{allen-zhu_linear_2016}, they interpreted the idea of Nesterov acceleration as a combinations of gradient descent and mirror descent.

@@

    \begin{theorem}[Proximal descent inequality]\label{thm:ppm_descent_ineq}
        Let $f: \RR^n \mapsto \overline \RR^n$ $\beta$ be strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
        For all $y \in \RR$ it verifies
        $$
            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
            - 
            \left(
                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
            \right)
            \le 
            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
        $$
        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
    \end{theorem}
    \begin{proof}
        See 
        \hyperref[appendix:proof_ppm_descent_lemma]
            {Appendix \ref*{appendix:proof_ppm_descent_lemma}}. 
    \end{proof}
    \begin{remark}
        We use this theorem to prove the convergence of the proximal point method. 
        Observe that when $\beta = 0$, this reduces to \cite[theorem 12.26]{bauschke_convex_2017}. 
    \end{remark}

@@

    \begin{definition}[AG proximal gradient PPM generic form]
    \label{def:ag_prox_grad_ppm}
        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
        With initial iterate $x_0, y_0$, 
        The generic form has iterates $x_t, y_t$ for all $t \in \N$ that satisfy: 
        $$
        \begin{aligned}
            x_{t + 1} &= \argmin_{x} \left\lbrace
                l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
                \Vert x - x_t\Vert^2
            \right\rbrace,
            \\
            y_{t + 1}&= 
            \argmin_{x}
            \left\lbrace
                l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
            \right\rbrace.
        \end{aligned}
        $$
    \end{definition}

@@

        It then produces the inequalities: 

@@

            \right)\Upsilon_{1, t + 1}^{\text{AG}}

@@

    \subsection{Recovering FISTA} 
        Let $\epsilon_i$ be given by
        \hyperref[thm:ag_generic_stepsize_constraints]
        {Theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ produces the relations 
        \begin{align*}
            a_{t + 1} &= (1/2)\left(
                1 + \sqrt{1 + 4 c_{t + 1}}
            \right), 
            \\
            c_{t + 1} &= a_t^2. 
        \end{align*}
        The recurrenct relations of $a_t$ indicates that it's the famous Nesterov momentum sequence. 
        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle \cite{beck_fast_2009-1}. 
        The following lemma uses $a_t$ to establish equivalence between the generic form of the algorithm and FISTA, a specific variant of accelerated gradient method. 
        \begin{lemma}[Similar triangle form]
            \quad \\
            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$,
            \hyperref[def:ag_prox_grad_generic]
            {Definition \ref*{def:ag_prox_grad_generic}}
            simplifies into 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
                \\
                x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
                \\
                y_{t + 1} &= 
                (1 + L\eta_{t + 1})^{-1}
                (
                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                ). 
            \end{align*}
            It is also equivalent to 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \\
                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
            \end{align*}
            And this is the FISTA algorithm. 
        \end{lemma}

@@

    \subsection{Recovering the accelerated gradient variant in Ryu's book}
        In this section we should that the following algorithm which appeared in Ryu \cite[chapter 12]{ryu_large-scale_2022}, the next definition present the algorithm in our notations. 
        \begin{definition}\label{def:ryu-ch12}
            Assume that $f$ is a L-Smooth convex function, with initial condition $x_0 = y_0$ an algorithm that generates iterates satisfying: 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1}\nabla f(y_t) 
                \\
                x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t) 
                \\
                y_{t + 1} &=
                \left(
                    1 - \frac{2}{t + 1}
                \right)z_{t+ 1}
                + 
                \left(
                    \frac{2}{t + 2}
                \right)x_{t + 1}, 
            \end{align*}
            achieves an optimal convergence rate. 
        \end{definition}

        \begin{lemma}
            Suppose that the generic form as given by 
            \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
            admits stepsize $\tilde \eta_t, \eta_t$ as
            \begin{align*}
                \tilde \eta_{t} &= \frac{t}{2L},
                \\
                \eta_t &= (t - 1)/(2L). 
            \end{align*}
            Then it's algebraically equivalent to 
            \hyperref[def:ryu-ch12]{Definition \ref*{def:ryu-ch12}}. 
        \end{lemma}
        \begin{proof}
            Observe $\tilde \eta_t = t/(2L)$ admits a linear growth rate. 
            If $\tilde \eta_i, \eta_i$ is a sequence that satisfies
            \hyperref[thm:ag_generic_stepsize_constraints]
            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
            then 
            \hyperref[thm:generic_ag_convergence]
            {Theorem \ref*{thm:generic_ag_convergence}}
            asserts a convergence rate of $\mathcal O(1/T^2)$ for $h(z_T) - h(x_*)$, where $x_*$ is a minimizer assumed to exist. 
            To show that the sequence satisfies 
            \hyperref[thm:ag_generic_stepsize_constraints]
            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
            first observe that $\epsilon_t = 0$ because 
            \begin{align*}
                L^{-1} + \eta_t 
                &= 
                L^{-1} + \frac{t - 1}{2L}
                \\
                &= \frac{t + 1}{2L}
                \\
                &= \tilde \eta_{t + 1}. 
            \end{align*}
            Therefore this is a similar triangle method. 
            Next observe that conditions showed in 
            \hyperref[thm:ag_generic_stepsize_constraints]
            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
            can be simplified in this context because the two equalities reduces to just one when $\epsilon_t =0$ for all $t \in \N$ by 
            \begin{align*}
                \tilde \eta_{t + 1}(\tilde \eta_{t + 1} - L^{-1}) 
                - L^{-1}\sigma_t &= 0
                \\
                \iff 
                \tilde \eta_{t + 1}\eta_t &= L^{-1}\sigma_t. 
            \end{align*}
            Hence it only requires to verify the equality $\tilde \eta_{t + 1}\eta_t = L^{-1} \sigma_t$. 
            With that we have 
            \begin{align*}
                \sigma_t &= \sum_{i = 1}^{t} \frac{i}{2L}
                \\
                &= \frac{1}{2L}\left(
                    \frac{t(t + 1)}{2}
                \right)
                \\
                &= \frac{t(1 + t)}{4L}
                \\
                \iff 
                L^{-1}\sigma_t &= 
                \frac{t(1 + t)}{4L}
            \end{align*}
            By definition of the stepsizes the LHS of the equality evaluates to
            \begin{align*}
                \tilde \eta_{t + 1} \eta_{t + 1}
                &= \frac{t + 1}{2L} \frac{t}{2L} 
                \\
                &= L^{-1}\sigma_t. 
            \end{align*}
        \end{proof}

    \subsection{Recovering Chambolle, Dossal 2015}

>>>>

\section{Introduction}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method (PPM) applied to an upper surrogate function, and then a lower surrogate function. 
    Inspired by the interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex whose proximal mapping can be evaluated exactly for algorithm implementations. 
    As a major extension, our work describes the method of proximal gradient using the PPM interpretations. We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof. We derive major variants of the Nesterov acceleation algorithm
    \cite{chambolle_convergence_2015}, \cite{beck_fast_2009}, \cite[Chapter 12]{ryu_large-scale_2022}
    of the accelerated gradient (AG) and find the match of the stepsize parameters in the PPM form.

    \par
    Some of the earlier examples for the extension of the Nesterov acceleration method make use of the classical analysis introduced by Nestrov. 
    It uses the Nesterov acceleration sequence. 
    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and a specific format of the Nesterov's estimating sequence to accomodate the proof. 
    In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
    It uses a lemma from Moreau envelope for the Lypunov analysis.
    The interpration allows choices of undetermined parameters to encompass several variants of the Nesterov accelerated gradient algorithm. 
    Ahn and Sra's approach is inspired by works from Defazio \cite{defazio_curved_2019}, Zeyuan and Lorenzo \cite{allen-zhu_linear_2016}. 
    Instead of a mirror descent step on the dual, they propose an alternative without the gradient of the dual. 
    \par
    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$ using Bregman Divergence. 
    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
    For a variant of accelerated gradient where the iterates converge (weakly in Hilbert space), see Chambolle and Dossal \cite{chambolle_convergence_2015}. 
    Extension such as the Harpen acceleration for the resolvent operator of a maximally monotone opreator in general is outside of the scope since it not all maximal monotone operator corresponds to a subgradient operator. 
    \par
    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
    The dynamical system interpretation of the algorithm leads to the valuable insight that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function. 
    In work by \cite{allen-zhu_linear_2016}, they interpreted the idea of Nesterov acceleration as a combinations of gradient descent and mirror descent.

@@

    \begin{theorem}[Proximal descent inequality]\label{thm:ppm_descent_ineq}
        Let $f: \RR^n \mapsto \overline \RR$ be $\beta$ strongly convex with $\beta \ge 0$, fix any $x \in \RR^n$, define $p = \hprox_f(x)$.
        For all $y \in \RR$ it verifies
        $$
            \left(f(p) + \frac{1}{2}\Vert x - p\Vert^2\right)
            - 
            \left(
                f(y) + \frac{1}{2}\Vert x - y\Vert^2 
            \right)
            \le 
            - \frac{(1 + \beta)}{2}\Vert y - p\Vert^2. 
        $$
        Recall: $\hprox_f(x) = \argmin_{u}\left\lbrace f(u) + \frac{1}{2}\Vert u - x\Vert^2 \right\rbrace$. 
    \end{theorem}
    \begin{proof}
        See 
        \hyperref[appendix:proof_ppm_descent_lemma]
            {Appendix \ref*{appendix:proof_ppm_descent_lemma}}. 
    \end{proof}
    \begin{remark}
        We use this theorem to prove the convergence of the proximal point method. 
        Observe that when $\beta = 0$, this reduces to \cite[theorem 12.26]{bauschke_convex_2017}. 
    \end{remark}

@@

    \begin{definition}[AG proximal gradient PPM generic form]
    \label{def:ag_prox_grad_ppm}
        Define $\eta_t, \tilde \eta_t$ to be strictly larger than zero for all $t \in \N$. 
        With initial iterate $x_0, y_0$, 
        The generic form has iterates $x_t, y_t$ for all $t \in \N$ that satisfy: 
        $$
        \begin{aligned}
            x_{t + 1} &= \argmin_{x} \left\lbrace
                l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
                \Vert x - x_t\Vert^2
            \right\rbrace,
            \\
            y_{t + 1}&= 
            \argmin_{x}
            \left\lbrace
                l_h(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
            \right\rbrace.
        \end{aligned}
        $$
    \end{definition}

@@

        Then it as inequalities: 

@@

            \right)\Upsilon_{2, t + 1}^{\text{AG}}

@@

    \subsection{Recovering FISTA} 
        Let $\epsilon_i$ be given by
        \hyperref[thm:ag_generic_stepsize_constraints]
        {Theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ produces the relations 
        \begin{align*}
            a_{t + 1} &= (1/2)\left(
                1 + \sqrt{1 + 4 c_{t + 1}}
            \right), 
            \\
            c_{t + 1} &= a_t^2. 
        \end{align*}
        The recurrenct relations of $a_t$ indicates that it's the famous Nesterov momentum sequence. 
        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle \cite{beck_fast_2009-1}. 
        The following lemma uses $a_t$ to establish equivalence between the generic form of the algorithm and FISTA, a specific variant of accelerated gradient method. 
        \begin{lemma}[Similar triangle form]\label{lemma:sim_triangle_form}
            \quad \\
            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$,
            \hyperref[def:ag_prox_grad_generic]
            {Definition \ref*{def:ag_prox_grad_generic}}
            simplifies into 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
                \\
                x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
                \\
                y_{t + 1} &= 
                (1 + L\eta_{t + 1})^{-1}
                (
                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                ). 
            \end{align*}
            It is also equivalent to 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \\
                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
            \end{align*}
            And this is the FISTA algorithm. 
        \end{lemma}

@@

    % \subsection{Recovering the accelerated gradient variant in Ryu's book}
    %     In this section we should that the following algorithm which appeared in Ryu \cite[chapter 12]{ryu_large-scale_2022}, the next definition present the algorithm in our notations. 
    %     \begin{definition}\label{def:ryu-ch12}
    %         Assume that $f$ is a L-Smooth convex function, with initial condition $x_0 = y_0$ an algorithm that generates iterates satisfying: 
    %         \begin{align*}
    %             z_{t + 1} &= y_t - L^{-1}\nabla f(y_t) 
    %             \\
    %             x_{t + 1} &= x_t - \frac{t + 1}{2L} \nabla f(y_t) 
    %             \\
    %             y_{t + 1} &=
    %             \left(
    %                 1 - \frac{2}{t + 1}
    %             \right)z_{t+ 1}
    %             + 
    %             \left(
    %                 \frac{2}{t + 2}
    %             \right)x_{t + 1}, 
    %         \end{align*}
    %         achieves an optimal convergence rate. 
    %     \end{definition}

    %     \begin{lemma}
    %         Suppose that the generic form as given by 
    %         \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
    %         admits stepsize $\tilde \eta_t, \eta_t$ as
    %         \begin{align*}
    %             \tilde \eta_{t} &= \frac{t}{2L},
    %             \\
    %             \eta_t &= (t - 1)/(2L). 
    %         \end{align*}
    %         Then it's algebraically equivalent to 
    %         \hyperref[def:ryu-ch12]{Definition \ref*{def:ryu-ch12}}. 
    %     \end{lemma}
    %     \begin{proof}
    %         Observe $\tilde \eta_t = t/(2L)$ admits a linear growth rate. 
    %         If $\tilde \eta_i, \eta_i$ is a sequence that satisfies
    %         \hyperref[thm:ag_generic_stepsize_constraints]
    %         {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    %         then 
    %         \hyperref[thm:generic_ag_convergence]
    %         {Theorem \ref*{thm:generic_ag_convergence}}
    %         asserts a convergence rate of $\mathcal O(1/T^2)$ for $h(z_T) - h(x_*)$, where $x_*$ is a minimizer assumed to exist. 
    %         To show that the sequence satisfies 
    %         \hyperref[thm:ag_generic_stepsize_constraints]
    %         {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    %         first observe that $\epsilon_t = 0$ because 
    %         \begin{align*}
    %             L^{-1} + \eta_t 
    %             &= 
    %             L^{-1} + \frac{t - 1}{2L}
    %             \\
    %             &= \frac{t + 1}{2L}
    %             \\
    %             &= \tilde \eta_{t + 1}. 
    %         \end{align*}
    %         Therefore this is a similar triangle method. 
    %         Next observe that conditions showed in 
    %         \hyperref[thm:ag_generic_stepsize_constraints]
    %         {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    %         can be simplified in this context because the two equalities reduces to just one when $\epsilon_t =0$ for all $t \in \N$ by 
    %         \begin{align*}
    %             \tilde \eta_{t + 1}(\tilde \eta_{t + 1} - L^{-1}) 
    %             - L^{-1}\sigma_t &= 0
    %             \\
    %             \iff 
    %             \tilde \eta_{t + 1}\eta_t &= L^{-1}\sigma_t. 
    %         \end{align*}
    %         Hence it only requires to verify the equality $\tilde \eta_{t + 1}\eta_t = L^{-1} \sigma_t$. 
    %         With that we have 
    %         \begin{align*}
    %             \sigma_t &= \sum_{i = 1}^{t} \frac{i}{2L}
    %             \\
    %             &= \frac{1}{2L}\left(
    %                 \frac{t(t + 1)}{2}
    %             \right)
    %             \\
    %             &= \frac{t(1 + t)}{4L}
    %             \\
    %             \iff 
    %             L^{-1}\sigma_t &= 
    %             \frac{t(1 + t)}{4L^2}
    %         \end{align*}
    %         By definition of the stepsizes the LHS of the equality evaluates to
    %         \begin{align*}
    %             \tilde \eta_{t + 1} \eta_{t + 1}
    %             &= \frac{t + 1}{2L} \frac{t}{2L} 
    %             \\
    %             &= L^{-1}\sigma_t. 
    %         \end{align*}
    %     \end{proof}

    % \subsection{Recovering Chambolle, Dossal 2015}
    %     In this section we show that the algorithm presented in the literature by Chambolle Dossal \cite{chambolle_convergence_2015} is an example of 
    %     Definition \ref*{def:ag_prox_grad_generic}. 
    %     The next definiton present the algorithm in our notations
    %     \begin{definition}\label{def:chamb_dossal}
    %         Assume that $h = f + g$ where $f$ is $L$-smooth, $f,g$ are convex. 
    %         Let $t_n = (n + a - 1)/a$ for all $t \in \N$, $a > 2$. 
    %         The algorithm by Chambolle Dossal has iterates $(x_n, y_n, z_n)$ satisfying for all $n \in \N$: 
    %         \begin{align*}
    %             z_{n + 1} &= y_n - L^{-1} \mathcal G_L(y_n), 
    %             \\
    %             x_{n + 1} &= z_n + t_{n +1} (z_{n + 1} - z_n), 
    %             \\
    %             y_{n + 1} &= \left(
    %                 1 - \frac{1}{t_{n + 1}}
    %             \right)z_{n + 1} + \left(
    %                 \frac{1}{t_{n + 1}}
    %             \right)x_{n + 1}. 
    %         \end{align*}
    %     \end{definition}
    %     \begin{lemma}
    %         Suppose that the generic form as given by 
    %         \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
    %         admits stepsize $\tilde \eta_t, \eta_t$ as
    %         \begin{align*}
    %             L\eta_n = t_n - 1,
    %             \\
    %             \tilde \eta_{n + 1} = L^{-1} + \eta_n. 
    %         \end{align*}
    %         Then it's algebraically equivalent to 
    %         \hyperref[def:chamb_dossal]{Definition \ref*{def:chamb_dossal}}. 
    %     \end{lemma}
    %     \begin{proof}
    %         By second equality: $\tilde \eta_{n + 1} = \eta_n + L^{-1}$, we can use 
    %         \hyperref[lemma:sim_triangle_form]{Lemma \ref*{lemma:sim_triangle_form}}. 
    %         Therefore, substituting $L\eta_n = t_n - 1$, $x_{n + 1}, y_{n + 1}$ in the generic form has 
    %         \begin{align*}
    %             x_{n + 1} &= 
    %             (1 + L\eta_n) z_{n + 1} - L\eta_n z_n
    %             \\
    %             & = 
    %             t_n z_{n + 1} + (1 - t_n) z_n 
    %             \\
    %             &= z_n + t_n(z_{n +1} - z_n)
    %             \\
    %             y_{n + 1} &= (1 + L\eta_{n + 1})^{-1} (L\eta_{n + 1} z_{n + 1} + x_{n + 1})
    %             \\
    %             &= t^{-1}_{n + 1} ((t_{n + 1} - 1)z_n + x_{n + 1})
    %             \\
    %             &= (1 - t_{n + 1}^{-1})z_{n + 1} + t^{-1}x_{n + 1}. 
    %         \end{align*}
    %         This is the same as
    %         \hyperref[def:chamb_dossal]{Definition \ref*{def:chamb_dossal}}. 
    %     \end{proof}
    %     \begin{remark}

    %     \end{remark}
